\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt] \huge Deep learning transcriptomic model for prediction of pan-drug chemotherapeutic sensitivity \\

### 2020-06-26 manuscript/manuscript.tex
updated conlcusion

% Conclusions
\section{Conclusions}
Using transcriptomic data from pan-cancer cell lines, two chemotherapeutic response clusters were identified via unsupervised learning in the form of k-means clustering. A feature selection algorithm was used to select a 300 gene subset which served as inputs to multiple neural networks. We determined that the network with 4 hidden layers was the most accurate model, producing a binary classifier to predict cell line therapy response with 91.7\% accuracy. Future studies will investigate the efficacy of our model to predict chemotherapy response in various cancer types and treatment contexts.

>>>>

% Conclusions
\section{Conclusions}
Using transcriptomic data from pan-cancer cell lines, two chemotherapeutic response clusters were identified via unsupervised learning in the form of k-means clustering. A feature selection algorithm was used to select a 300 gene subset which served as inputs to multiple neural networks. We determined that the network with 10 hidden layers was the most accurate model, producing a binary classifier to predict cell line therapy response with 95.4\% accuracy. Future studies will investigate the efficacy of our model to predict chemotherapy response in various cancer types and treatment contexts.
